Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-15 ieee_paper.tex
loading the matrix nnz

>>>>

The values from the non zero element in the matrix are the simplest to
load. One can load the 16 floating point values for the 4 non zero of
the matrix at once. The 4 floats coming from the four matrices for
each non zero are naturally grouped within each lane of the SIMD
vector. One can use lane permutation to broad a lane to take the whole
vector. So one 1 permutations and a quarter load are necessary to put
the data of the matrix in the required format.
